\EVOSUITE at the SBST 2017 Tool Competition

### 2018-01-31 papers/sbst18/mainTable.tex
updated table

BCEL-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &

@@

 & mocking\\ 
BCEL-10 & 63.9\% & 56.0\%\\ 
BCEL-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{12}{l}{Failed to use Mockito on interface java.io.DataInput}\\ 
 & \multicolumn{12}{l}{java.lang.ClassCastException: java.lang.Byte
   cannot be cast to java.lang.Short at org.evosuite.testcase.statements.FunctionalMockStatement\$1.fixBoxing(FunctionalMockStatement.java:849)}\\ 
BCEL-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Minimisation and junit check timeout; test
   suite's coverage: resulting coverage 74\% } \\ 
BCEL-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{no error, evosuite reported coverage 42\%}\\ 
BCEL-6 & 72.2\% & 78.0\%\\ 
BCEL-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                           \cellcolor{light-gray} \textcolor{black}{0.0}\%& \multicolumn{13}{l}{ERROR FunctionalMockStatement - IAE on public java.lang.String org.apache.bcel.classfile.ConstantPool.getConstantString(int,byte) throws org.apache.bcel.classfile.ClassFormatException> when called with [0, null}\\ 
BCEL-8 & 95.8\% & 96.9\%\\ 
BCEL-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on interface java.io.DataInput: java.lang.Byte cannot be cast to java.lang.Short}\\ 
FREEHEP-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Resulting test suite's coverage: 98\%;
   minimisation timed out}\\ 
FREEHEP-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Resulting test suite's coverage: 83\%;
   JUNIT\_CHECK timed out}\\ 
FREEHEP-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
&  \multicolumn{13}{l}{Resulting test suite's coverage: 85\%; no error} \\ 
FREEHEP-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 &  \multicolumn{13}{l}{Resulting test suite's coverage: 81\%; no
   error, flaky tests}\\ 
FREEHEP-4 & 60.3\% & 24.3\%\\ 
FREEHEP-5 & 69.1\% & 84.4\%\\ 
FREEHEP-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
  &  \multicolumn{13}{l}{Resulting test suite's coverage: 87\%; no
   error, flaky tests}\\
FREEHEP-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
                                                              \cellcolor{light-gray} \textcolor{black}{0.0}\%   &  \multicolumn{13}{l}{Resulting test suite's coverage: 81\%; no
   error, flaky tests}\\ 
FREEHEP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{87\% coverage; Permissions denied during test execution:  java.lang.RuntimePermission: writeFileDescriptor: 7}\\ 
FREEHEP-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{57\% coverage; minimisation and junit\_check
   time out}\\ 
GSON-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &

 & \multicolumn{13}{l}{test suite's coverage: 58\% .  Permissions denied during test execution:  java.lang.RuntimePermission: writeFileDescriptor: 1} \\ 
GSON-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 &  \multicolumn{13}{l}{java.lang.RuntimeException: not implemented:
   class sun.reflect.generics.reflectiveObjects.TypeVariableImpl at com.googlecode.gentyref.GenericTypeReflector.isSuperType(GenericTypeReflector.java:218)} \\ 
GSON-2 & 33.5\% & 31.1\%\\ 
GSON-3 & 82.5\% & 83.9\%\\ 
GSON-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{31\% coverage; no errors}\\ 
GSON-5 & 33.3\% & 36.5\%\\ 
GSON-6 & 90.7\% & 71.8\%\\ 
GSON-7 & 81.6\% & 94.0\%\\ 
GSON-8 & 90.7\% & 75.8\%\\ 

@@

 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory}\\ 
IMAGE-2 & 85.0\% & 99.0\%\\ 
IMAGE-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &

@@

 & \multicolumn{13}{l}{Multiple errors like: ERROR ClassStateSupport - Could not initialize org.apache.commons.imaging.formats.tiff.TiffImageMetadata}\\ 
IMAGE-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &

@@

& \multicolumn{13}{l}{coverage 76\%; JUNIT\_CHECK timed out; Permissions denied during test execution: java.lang.RuntimePermission: writeFileDescriptor: 3}
  \\ 
JXPATH-1 & 27.2\% & 25.4\%\\ 
JXPATH-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &

@@

 & \multicolumn{13}{l}{coverage 76\%; some errors (java.lang.ClassNotFoundException:
   Class not found: org/jdom/Element: java.lang.NullPointerException:
   Class not found org/jdom/Element); flaky tests}\\ 
JXPATH-2 & 81.4\% & 70.5\%\\ 
JXPATH-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{coverage 76\%; some errors (ERROR ClassStateSupport - Could not initialize org.apache.commons.jxpath.JXPathContextFactory); flaky tests}\\ 
JXPATH-4 & 81.4\% & 75.0\%\\ 
JXPATH-5 & 92.0\% & 92.9\%\\ 
JXPATH-6 & 93.5\% & 90.0\%\\ 
JXPATH-7 & 10.9\% & 7.7\%\\ 
JXPATH-8 & 53.3\% & 42.8\%\\ 
JXPATH-9 & 56.1\% & 27.9\%\\ 
LA4J-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{coverage 75\%, JUNIT\_CHECK timed out}\\ 
LA4J-10 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Mocking problem: ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator: tried to access class org.la4j.iterator.CursorIterator from class org.la4j.iterator.VectorIterator\$MockitoMock}\\ 
 & \multicolumn{13}{l}{same as above}\\ 
LA4J-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Coverage 73\%, minimisation and junit check
   timed out}\\ 
LA4J-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Coverage 88\%; minimisation timeout, errors compiling and checking tests(ERROR ClassStateSupport - Could not initialize org.la4j.iterator.JoinFunction)}\\ 
LA4J-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
 & \multicolumn{13}{l}{Coverage 55\%; search, minimisation and writing tests timed out}\\ 
 & \multicolumn{13}{l}{Mocking problem: ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator: tried to access class org.la4j.iterator.CursorIterator from class org.la4j.iterator.VectorIterator\$MockitoMock}\\ 
LA4J-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
& \multicolumn{13}{l}{Resulting test suite's coverage: 57\%; timeout when
  writing tests}\\ 
LA4J-8 & 75.0\% & 70.0\%\\ 
LA4J-9 & 85.1\% & 29.8\%\\ 
OKHTTP-1 & 7.7\% & 5.6\%\\ 
OKHTTP-2 & 50.0\% & 50.0\%\\ 
OKHTTP-3 & 75.8\% & 69.0\%\\ 
OKHTTP-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
& \multicolumn{13}{l}{Coverage 62\%; Multiple errors (eg ERROR ConcreteClassAnalyzer - Problem for okhttp3.internal.http.HttpHeaders. Class not found: okhttp3.MultipartBody)}\\ 
OKHTTP-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
& \multicolumn{13}{l}{Coverage 48\%; problem executing tests: java.security.SecurityPermission:  createAccessControlContext: 2 javax.security.auth.AuthPermission: getSubject: 21}\\ 
OKHTTP-6 & 84.3\% & 86.4\%\\ 
OKHTTP-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &
&  \multicolumn{13}{l}{Coverage 40\%; error Compiling and checking tests}\\ 
& \multicolumn{13}{l}{Classpath problem? Caused by: java.lang.ClassNotFoundException: Class 'okio/Buffer.class' should be in target project, but could not be found!}\\ 
RE2J-1 & 56.5\% & 39.4\%\\ 
RE2J-2 & 92.9\% & 66.7\%\\ 
RE2J-3 & 42.9\% & 39.7\%\\ 
RE2J-4 & 92.7\% & 88.0\%\\ 
RE2J-5 & 68.2\% & 41.7\%\\ 
RE2J-6 & 85.1\% & 68.3\%\\ 
RE2J-7 & 39.5\% & 35.2\%\\ 
RE2J-8 & 91.8\% & 82.6\%\\ 

@@

Average  &  32.9\% &  29.1\%\\ 

>>>>

BCEL-1 & 54.7\% & 47.9\%\\ 
BCEL-10 & 62.5\% & 56.0\%\\ 
BCEL-2 & 1.2\% & 0.8\% & \multicolumn{13}{l}{Resulting test suite's coverage: 34\% (average coverage for all fitness functions)}\\ 
& \multicolumn{13}{l}{org.evosuite.shaded.org.mockito.exceptions.misusing.InvalidUseOfMatchersException: 
Misplaced or misused argument matcher detected here}\\ 
BCEL-4 & 80.8\% & 80.5\%\\ 
BCEL-5 & 37.5\% & 63.8\%\\ 
BCEL-6 & 59.3\% & 76.0\%\\ 
BCEL-7 & 60.0\% & 50.0\%\\ 
BCEL-8 & 95.8\% & 90.6\%\\ 
BCEL-9 & 81.1\% & 67.5\%\\ 
FREEHEP-1 & 93.1\% & 42.2\%\\ 
FREEHEP-10 & 95.8\% & 69.6\%\\ 
FREEHEP-2 & 76.6\% & 5.7\%\\ 
FREEHEP-3 & 55.6\% & 62.1\%\\ 
FREEHEP-4 & 46.8\% & 22.2\%\\ 
FREEHEP-5 & 70.9\% & 54.1\%\\ 
FREEHEP-6 & 59.3\% & 27.0\%\\ 
FREEHEP-7 & 81.2\% & 77.2\%\\ 
FREEHEP-8 & 93.1\% & 74.7\%\\ 
FREEHEP-9 & 29.7\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%
& \multicolumn{13}{l}{Resulting test suite's coverage: 36\%; ERROR ClassStateSupport - Could not initialize org.freehep.math.minuit.ModularFunctionMinimizer}\\ 
GSON-1 & 63.9\% & 41.7\%\\ 
GSON-10 & 58.5\% & 39.0\%\\ 
GSON-2 & 33.5\% & 34.8\%\\ 
GSON-3 & 77.5\% & 81.6\%\\ 
GSON-4 & 31.4\% & 24.2\%\\ 
GSON-5 & 29.3\% & 34.8\%\\ 
GSON-6 & 86.0\% & 72.6\%\\ 
GSON-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% &

@@

GSON-8 & 86.0\% & 70.2\%\\ 

@@

 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.apache.commons.imaging.formats.tiff.write.TiffOutputDirectory: tried to access class org.apache.commons.imaging.formats.tiff.write.TiffOutputItem}\\ 
IMAGE-2 & 88.3\% & 99.0\%\\ 
IMAGE-3 & 57.0\% & 32.5\%\\ 
IMAGE-4 & 80.6\% & 73.9\%\\ 
JXPATH-1 & 27.5\% & 25.4\%\\ 
JXPATH-10 & 40.8\% & 33.5\%\\ 
JXPATH-2 & 82.6\% & 72.7\%\\ 
JXPATH-3 & 73.4\% & 83.7\%\\ 
JXPATH-4 & 78.4\% & 72.8\%\\ 
JXPATH-5 & 90.0\% & 92.9\%\\ 
JXPATH-6 & 93.5\% & 96.0\%\\ 
JXPATH-7 & 24.5\% & 10.8\%\\ 
JXPATH-8 & 52.7\% & 42.8\%\\ 
JXPATH-9 & 68.4\% & 27.9\%\\ 
LA4J-1 & 75.4\% & 81.4\%\\ 
LA4J-10 & 86.4\% & 67.9\%\\ 

@@

                                                           & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.RowMajorMatrixIterator}\\ 
LA4J-3 & 67.1\% & 37.6\%\\ 
LA4J-4 & 84.8\% & 74.7\%\\ 
LA4J-5 & 52.9\% & 34.5\%\\ 

@@

 & \multicolumn{13}{l}{ERROR FunctionalMockStatement - Failed to use Mockito on class org.la4j.iterator.VectorIterator}\\ 
LA4J-7 & 64.3\% & 40.6\%\\ 
LA4J-8 & 76.5\% & 93.6\%\\ 
LA4J-9 & 94.3\% & 30.4\%\\ 
OKHTTP-1 & 7.2\% & 5.6\%\\ 
OKHTTP-2 & 50.0\% & 44.1\%\\ 
OKHTTP-3 & 74.2\% & 67.6\%\\ 
OKHTTP-4 & 58.1\% & 53.5\%\\ 
OKHTTP-5 & 3.0\% & 4.0\%\\ 
OKHTTP-6 & 77.1\% & 76.3\%\\ 
OKHTTP-7 & 46.9\% & 27.0\%\\ 

@@

 & \multicolumn{13}{l}{Caused by: java.lang.ClassNotFoundException:
   Class okio/Buffer.class should be in target project, but could not be found!}\\ 
RE2J-1 & 54.5\% & 36.9\%\\ 
RE2J-2 & 93.8\% & 71.6\%\\ 
RE2J-3 & 50.0\% & 37.9\%\\ 
RE2J-4 & 97.9\% & 90.6\%\\ 
RE2J-5 & 57.6\% & 29.1\%\\ 
RE2J-6 & 83.5\% & 71.2\%\\ 
RE2J-7 & 47.1\% & 27.8\%\\ 
RE2J-8 & 91.8\% & 79.0\%\\ 

@@

Average  &  57.9\% &  47.3\%\\ 
